Compositional Quantitative Resource Analysis of C Programs

### 2014-06-17 paper/main.tex
uniformize notations
update discussion on \circ

\and \Rule{S:IfThen}
{  (\state, S_1) \Downarrow_{(q, q')} O
\\ {\sf istrue}~\llbracket C \rrbracket_\state
}
{ (\state, \code{if}(C)~S_1~\code{else}~S_2)
  \Downarrow_{M_c^1 \cdot (q, q')} O
}

\and \Rule{S:IfElse}
{  (\state, S_2) \Downarrow_{(q, q')} O
\\ {\sf isfalse}~\llbracket C \rrbracket_\state
}
{ (\state, \code{if}(C)~S_1~\code{else}~S_2)
  \Downarrow_{M_c^2 \cdot (q, q')} O
}

@@

The busy result is also useful to handle diverging programs with big-step
judgements.  In case a program does not terminate, there is no heap $H'$
such that $(H, S)\Downarrow_{(q, q')} H'$.  The only possible way to
conclude a big-step judgement is to use the {\sc S:Abort} rule at some
point in the computation.  One alternative to this technique is to use
coinductive semantics~\cite{Leroy-coind}, however, using the busy
result is precise enough in our setting of quantitative resource analysis and
allows to have only one soundness proof for both unsafe and
non-terminating programs.  Indeed, stating a result for
$(H, S) \Downarrow_{(q,q')} \circ$ covers unsafe programs, diverging
programs, and partial computations at the same time.

>>>>

\and \Rule{S:IfThen}
{  (\state, S_1) \Downarrow_{(q, q')} O
\\ {\sf istrue}~\llbracket e \rrbracket_\state
}
{ (\state, \code{if}(e)~S_1~\code{else}~S_2)
  \Downarrow_{M_c^1 \cdot (q, q')} O
}

\and \Rule{S:IfElse}
{  (\state, S_2) \Downarrow_{(q, q')} O
\\ {\sf isfalse}~\llbracket e \rrbracket_\state
}
{ (\state, \code{if}(e)~S_1~\code{else}~S_2)
  \Downarrow_{M_c^2 \cdot (q, q')} O
}

@@

The busy result is also useful to handle diverging programs with big-step
judgements.  In case a program does not terminate, it is impossible to
derive $(\state, S)\Downarrow_{(q, q')} O$ with $O \neq \circ$.  The only
possible way to conclude a big-step judgement is to use the {\sc S:Abort}
rule at some point in the computation.  One alternative to this technique
is to use coinductive semantics~\cite{Leroy-coind}, however, using the busy
result prevents duplication and allows to have only one soundness proof for
both unsafe and non-terminating programs.  Indeed, stating a result for
$(\sigma, S) \Downarrow_{(q,q')} \circ$ covers unsafe programs, diverging
programs, and partial computations at the same time.
